Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-17 krs-survey.tex
More on logical formalism, added a section on expressive power

@@

\subsubsection{Introduction: main logic formalisms}

@@

The family of \emph{description logics}~\cite{Baader2008} also play an
important role. It is a subset of the first-order logic, with some extensions
in second-order logic. Description logics are notable because most of them are
known to be decidable. In description logic, axioms are build from
\emph{concepts}, \emph{roles} (that are unary or binary predicates) and
\emph{individuals}. The W3C OWL-DL standard is a widely-used language to describe
domain with the description logic.

\emph{Modal logics}, that allow for statement qualification
like \emph{possibility} or \emph{necessity}, have been shown to be closely
related to description logics.

@@

@@

@@

>>>>

Table~\ref{table|contribution-by-systems}, at the end of the article,
summarizes all these features with the main domain of contribution of each
surveyed KRS.

@@

\subsubsection{Introduction: Main Logic Formalisms}

@@

The family of \emph{description logics}~\cite{Baader2008} also play an
important role. It is a subset of the first-order logic, with some extensions
in second-order logic. Description logics are notable because most of them are
known to be decidable. In description logic, axioms are build from
\emph{concepts}, \emph{roles} (that are unary or binary predicates) and
\emph{individuals}. The W3C OWL-DL standard is a widely-used language to describe
domains with the description logic.

Because Description Logics have been originally created from the perspective of
a \emph{knowledge representation language} and not a logic language, their
terminology (\emph{concept} or \emph{class}, \emph{role} or \emph{property},
\emph{individual},...) is well-suited to knowledge description and we may use
it in the remaining of this paper outside of the strict context of  Description
Logics.

\emph{Modal logic}, that allow for statement qualification like
\emph{possibility} or \emph{necessity}, have been shown to be closely related
to description logics. Modal logic allows to represent conveniently parallel
possible worlds and facts like ``the robot knows \emph{that the human knows}
how to read a recipe''.

@@

\emph{Temporal logic} are designed to represent and manipulate assertions whose
truth value may vary in time.

@@

Note that most of these logic formalisms are still active research field by
their own, and practical considerations (especially the availability of
reasoners performant enough for on-line use on a robot) often constraint the
choice of a logical formalism and a level of expressive power.

@@

\subsubsection{Expressive Power}

Logical formalisms each bring a certain level of expressive power. For
instance, the following classical syllogism can not be represented in
propositional logic because of the use of \emph{universal quantification}:

\begin{quote}
\begin{enumerate}
    \item All men are mortal,
    \item Socrates is a man,
    \item Therefore, Socrates is mortal
\end{enumerate}
\end{quote}

However, the following weak version of the syllogism can be represented in
propositional logic:

\begin{quote}
\begin{enumerate}
    \item If Socrates is a man, then Socrates is mortal,
    \item Socrates is a man,
    \item Therefore, Socrates is mortal
\end{enumerate}
\end{quote}

Generally speaking, expressive power comes at the cost of ease of
\emph{satisfiability} and \emph{consistency}\footnote{We precise these concepts
at section~\ref{sect|reasoning}.} tests, possibly leading to undecidable formal
systems, \ie systems where it is proven that a proposition can not be decided
to be true or false.

The relationship between expressive power and the complexity of reasoning problem that
follow has been partially formalized for Description Logics.
Zolin~\cite{ZolinDLComplexityNavigator} maintains a ``complexity navigator''
for Description Logics that allows to conveniently explore this relationship
and indexes most of the litterature on that subject.
